Numerical simulation and entropy dissipative cure of the carbuncle instability for the shallow water circular hydraulic jump

### 2021-03-07 numerics_paper/version2/numerical_chj.tex
remove older definition
Simplify notation in section 3.1.

In our implementation, we consider
{\color{blue}

@@

To compute these integrals, we first split $\partial S_i$ into its faces $\{\f_i\in\partial S_i\}$.
Let $|\f_i|$ be the length of $\f_i$, $\bar Q_{\f_i}$ be the average of $Q$ 
from both sides of $\f_i$ and $\bfn_{\f_i}$ be the unit vector normal to $\f_i$ 
pointing outward from cell $i$.
Then, we use

@@

  \left|\sum_{\f_i\in\partial S_i} |\f_i|
  \left[\entvar(\bfq_i)\cdot \left(\bfn_{\f_i} \cdot \bff\left(\bar Q_{\f_i}\right)\right)-\bfn_{\f_i} \cdot\entflux \left(\bar Q_{\f_i}\right)\right] \right|,

@@

and 

@@

  \left|\sum_{\f_i\in\partial S_i}|\f_i|\left(\bfn_{\f_i}\cdot\bff\left(\bar Q_{\f_i}\right)\right)_k\right|
  +\left|\sum_{\f_i\in \partial S_i} |\f_i| \bfn_{\f_i}\cdot\entflux\left(\bar Q_{\f_i}\right) \right|,

@@

and $d$ is the number of physical dimensions.}
{\color{red}
\begin{subequations}\label{Ri_and_Di_tmp}
  \approx 
and 
  \sum_{k=1}^{d+1}|\entvar_k(\bfq_i)|\left|\int_{\partial S_i}\left(\bfn_i(s)\cdot\bff(q)\right)_kd\bfs\right|
  +\left|\int_{\partial S_i}\bfn_i(s)\cdot\entflux(q) d\bfs\right|,
where $\bfn_i$ denotes the unit vector normal to $\partial S_i$ pointing outward from cell $i$,
$(z)_k$ denotes the $k$-th component of $z\in\mathbb{R}^{d+1}$, 

@@

In the integrands of \eqref{Ri_and_Di_tmp}, $q$ is the average of $Q$ 
from each side of the boundary $\partial S_i$.}

>>>>

In our implementation, we use the approximation

@@

To compute the boundary integrals, we approximate $q$ on each cell edge $\f_{ij}$ by the average of the two
neighboring cell averages $\bar Q_{ij} = (Q_i+Q_j)/2$, resulting in

@@

  \left|\sum_{\f_{ij}\in\partial S_i} |\f_{ij}|
  \left[\entvar(\bfq_i)\cdot \left(\bfn_{ij} \cdot \bff\left(\bar Q_{ij}\right)\right)-\bfn_{ij} \cdot\entflux \left(\bar Q_{ij}\right)\right] \right|,

@@

where $\bfn_{ij}$ and $|\f_{ij}|$ are
the unit outward-facing normal and edge length of edge $\f_{ij}$, respectively.
The normalization factor is similarly computed as

@@

  \left|\sum_{\f_{ij}\in\partial S_i}|\f_{ij}|\left(\bfn_{ij}\cdot\bff\left(\bar Q_{ij}\right)\right)_k\right|
  +\left|\sum_{\f_i\in \partial S_i} |\f_{ij}| \bfn_{ij}\cdot\entflux\left(\bar Q_{ij}\right) \right|,

@@

@@

%\begin{subequations}\label{Ri_and_Di_tmp}
%\begin{align}
%  R_i 
%  \approx 
%  \left|\entvar(\bfq_i)\cdot \int_{S_i}\nabla\cdot \bff(q)d\bfx
%  -\int_{S_i}\nabla\cdot\entflux(q) d\bfx\right| 
%  = 
%  \left|\entvar(\bfq_i)\cdot \int_{\partial S_i}\bfn_i(s) \cdot \bff(q) d\bfs
%  -\int_{\partial S_i}\bfn_i(s)\cdot\entflux(q) d\bfs\right|, 
%\end{align}
%and 
%\begin{align}
%  D_i 
%  = 
%  \sum_{k=1}^{d+1}|\entvar_k(\bfq_i)|\left|\int_{\partial S_i}\left(\bfn_i(s)\cdot\bff(q)\right)_kd\bfs\right|
%  +\left|\int_{\partial S_i}\bfn_i(s)\cdot\entflux(q) d\bfs\right|,
%\end{align}
%\end{subequations}
%where $\bfn_i$ denotes the unit vector normal to $\partial S_i$ pointing outward from cell $i$,
%$(z)_k$ denotes the $k$-th component of $z\in\mathbb{R}^{d+1}$, 
%and $d$ is the number of physical dimensions.  
%In the integrands of \eqref{Ri_and_Di_tmp}, $q$ is the average of $Q$ 
%from each side of the boundary $\partial S_i$.
